Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-16 WSSSPE4_report/WSSSPE4_report.tex
... updated lightning talks again (19 submissions, if 19 presented)
lightning talk section done!

Submissions to WSSSPE4 comprised
18 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
19 lightning talks,
4 idea papers,
3 position papers,
2 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.
The paper and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

\note{Kyle Niemeyer will write this}

There were 19 lightning talks presented at WSSSPE4, as follows.
%
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
%
\begin{itemize}[itemsep=1ex]
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Sufi, Community Lead at the Software Sustainability Institute (SSI), discussed
    the SSI Fellowship program and the fellows, including their
    demographic breakdown and domains of practice. This program came about
    based on the institute's desire to integrate with the research community---thus
    inspiring change from within---rather than preach to it. Five SSI fellows
    attended WSSSPE4.

>>>>

Submissions to WSSSPE4 comprised
19 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
19 lightning talks,
4 idea papers,
3 position papers,
2 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.
The paper and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

There were 19 lightning talks presented at WSSSPE4, as follows (in order of
presentation).
%
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
%
\begin{itemize}[itemsep=1ex]
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Sufi, Community Lead at the Software Sustainability Institute (SSI), discussed
    the SSI Fellowship program and the fellows, including their
    demographic breakdown and domains of practice. This program came about
    based on the institute's desire to integrate with the research community---thus
    inspiring change from within---rather than preach to it. Five SSI fellows
    attended WSSSPE4.
